---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nychex

<!-- badges: start -->
<!-- badges: end -->

nychex provides tessellated hexagonal tile maps for New York City
administrative geographies. Each polygon in the source geography is
represented by a single hexagonal tile, arranged to approximate the
overall spatial layout of the city.

## Installation

You can install the development version of nychex from
[GitHub](https://github.com/kjhealy/nychex) with:

``` r
# install.packages("pak")
pak::pak("kjhealy/nychex")
```

## Example

```{r hex-map, fig.width = 8, fig.asp = 1.2, dpi = 150}
library(ggplot2)
library(nychex)

ggplot(nyc_nta20_hex_sf) +
  geom_sf(aes(fill = boro_name), color = "white", linewidth = 0.3) +
  scale_fill_brewer(palette = "Set2") +
  labs(fill = "Borough") +
  theme_void()
```

```{r hex-map-labeled, fig.width = 10, fig.asp = 1.2, dpi = 150}
ggplot(nyc_nta20_hex_sf) +
  geom_sf(aes(fill = boro_name), color = "white", linewidth = 0.3) +
  geom_sf_text(aes(label = nta_abbrev), size = 1.8) +
  scale_fill_brewer(palette = "Set2") +
  labs(fill = "Borough") +
  theme_void()
```

Borough outlines are also available via `nyc_boro_hex_outlines_sf`,
with separate outlines for Brooklyn and Queens:

```{r hex-outlines, fig.width = 8, fig.asp = 1.2, dpi = 150}
ggplot() +
  geom_sf(
    data = nyc_nta20_hex_sf,
    aes(fill = boro_name),
    color = "white",
    linewidth = 0.2,
    alpha = 0.3
  ) +
  geom_sf(
    data = nyc_boro_hex_outlines_sf,
    aes(color = boro_name),
    fill = NA,
    linewidth = 0.8
  ) +
  scale_fill_brewer(palette = "Set2") +
  scale_color_brewer(palette = "Set2") +
  labs(fill = "Borough", color = "Borough") +
  theme_void()
```
